### 2022-05-18 main/chapter_2ljets.tex
begin context, author credits

Our main result is the content of Figure~\ref{fig:2ljets_summary}, which shows
the data in all main regions of this analysis, along with the regions' names,
and post-fit background expectations.
This figure illustrates the background-only part of a \clown{likelihood}
model which is extended with signals to test alternative models.

@@

\paragraph{My contributions}
\begin{itemize}
\item Design, implementation and execution of the electroweak part of the analysis.
\item Service as `analysis contact' from January to October 2020.
\item Production of main data inputs for all three analyses
and the RJR $3\ell$ search \TODO{cite}.
Production of all systematic variations for the background samples;
other group members assisted with the central background sample.
Production of all electroweak signal samples and their systematic variations.
\item Integration with ATLAS combinations and pMSSM scan efforts by
performing their validation studies and serializing the analysis results.
\item Preparation of electroweak results for publication in the paper \TODO{cite} and the
public HEPData record~\cite{maguire2017hepdata}.
\end{itemize}

\clearpage
\FloatBarrier
\section{Context}
% previous results on 2(/3)L from ATLAS
% other constraints on these models from ATLAS/CMS
% previous region design, motivation for this work

@@

\subsection{b-tagging}
\label{sec:btagging}
% with $\pt > 20$ GeV,
% where the tag is taken on the mv2c10 classifier at the $77\%$ working point.

>>>>

Our main result is the content of Figure~\ref{fig:2ljets_summary}, which shows
the data in all main regions of this analysis, along with the regions' names,
and post-fit background expectations.
This figure illustrates the background-only part of a \heplikelihood
model which is extended with signals to test alternative models.

@@

\paragraph{Contributions}
My contributions the the analysis are listed here.
\begin{itemize}
\item Design, implementation and execution of the electroweak part of the analysis.
\item Service as `analysis contact' from January to October 2020.
\item Production of main data inputs for all three analyses
and the RJR $3\ell$ search \TODO{cite}.
Production of all systematic variations for the background samples;
other group members assisted with the central background sample.
Production of all electroweak signal samples and their systematic variations.
\item Integration with ATLAS combinations and pMSSM scan efforts by
performing their validation studies and serializing the analysis results.
\item Preparation of electroweak results for publication in the paper \TODO{cite} and the
public HEPData record~\cite{maguire2017hepdata}.
\end{itemize}
Except where specified, I produced all figures presented in this thesis.
Many plotting scripts, however, are modified from versions inherited from
many \atlas\ members past and present to whom I am grateful.

Of the large collaboration involved in this project, a great deal of credit is
due to the following colleagues, labelled with their primary focus within
the $\twoljets$ search effort:
Knut Oddvar Vadla (electroweak),
Sarah Williams (electroweak),
Jason Lea Oliver (RJR),
Abhishek Sharma (RJR),
Jonathan Long (strong),
Arka Santra (strong),
Matt Zhang (strong),
Yumeng Cao (various),
Eirik Gramstad (fake/non-prompt leptons),
Benjamin Henry Hooberman (leadership).
Cheers.

\clearpage
\FloatBarrier
\section{Context}
% previous results on 2(/3)L from ATLAS
% other constraints on these models from ATLAS/CMS
% previous region design, motivation for this work
Previous searches studied this two-lepton + jets + $\ptmiss$ selection
in different or smaller data-sets in \atlas.
This project serves to update those results with the full LHC Run 2 data-set,
which contains $139~\mathrm{fb}^{-1}$ of usable proton-proton collisions at
$13~\eV[T]$ collision energy.

Increased quantity of data allows more options for this search.
Together with lessons learned from the previous searches, this is not only
an update but a chance for improvement.

This paper focusses solely on $\twoljets$ data and analyses them in the three
distinct RJR, electroweak, and strong parts.
Each part has precedent from previous searches which were conducted and
published separately with other work.
A decision was made for full Run 2 to group the searches by targetted physics,
rather than by method or targetted physical models.

The remainder of this section describes the specific history and motivations
for each of the RJR, electroweak and strong sub-projects in this search.

\subsection{RJR}
Recursive Jigsaw Reconstruction, abbreviated as RJR, is a method for
interpreting particle data as arising from user-specified decay trees.
The $\twoljets$ RJR analysis uses two C1N2 decay trees which are displayed in
Figure~\ref{fig:2ljets_rjr_decay_trees}.

\subsection{Electroweak}

\subsection{Strong}

@@

\subsection{$b$-tagging}
\label{sec:btagging}
% with $\pt > 20$ GeV,
% where the tag is taken on the mv2c10 classifier at the $77\%$ working point.
